---
title: "Phenology data 2016"
author: "Li Zhang and Aud Halbritter"
date: "1st. November 2016"
output: ioslides_presentation
---

## Questions and hypothesis

1. Do alpine grassland species respond in their phenology to warming?
2. Do species from different function groups / flowering time respond differently to warming?
3. Do species respond differ in their phenological in OTC vs. transplants?
4. How plastic are species in response to warming and cooling?


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, fig.height = 5.5, fig.width = 8)
knitr::read_chunk("Important Figures.R")

```

```{r loadPhenology}
```

```{r setTheme}
th <- theme_bw(base_size = 14)

```

## Community approach
```{r peakCommunity, eval = TRUE}

```

## Community approach
```{r durationCommunity, eval = TRUE}

```

## Functional Traits

```{r,  echo=FALSE}
# PeakFounctionalGroup + theme_grey(base_size = 20) + theme(legend.title=element_blank()) + ggtitle("Peak time of different FunctionalGroup")
```

```{r,  echo=FALSE}
# TimeFounctionalGroup + theme_grey(base_size = 20) + theme(legend.title=element_blank()) + ggtitle("time between neighboring stages")
```

## Compare the treatments

```{r, echo=FALSE}

#firstbudSpecies + theme_grey(base_size = 5) + theme(legend.title=element_blank())# + ggtitle("First buds")

```

```{r, echo=FALSE}
#TimeFsSpecies + theme_grey(base_size = 5) + theme(legend.title=element_blank())# + ggtitle("...")
```

## Things to discuss

- How to define the flowering time to "early","late" stage ?
- How to define the alpine species according the elevation span?


## Next steps

- Calculate microclimate effects of different warming methods
- How species respond to experimental temperature?
- Gap of the H site climate data.


