---
title: "Phenology data 2016"
author: "Li Zhang and Aud Halbritter"
date: "5th November 2016"
output: ioslides_presentation
---

## Questions and hypothesis

1. Do alpine grassland species respond in their phenology to warming?
2. Do species from different function groups / flowering time respond differently to warming?
3. Do species respond differ in their phenological in OTC vs. transplants?
4. How plastic are species in response to warming and cooling?


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8)
knitr::read_chunk("Important Figures.R")

```

```{r loadPhenology}
pheno.long %>%
  mutate(pheno.stage = factor(pheno.stage, levels = c("b", "f","s","r","bf","fs","sr")))


```

```{r setTheme}
th <- theme_bw(base_size = 14)

```

```{r loadTrait}

```


```{r loadTreatment}

```


## Community approach
```{r PeakCommunity, eval = TRUE}

```

## Community approach
```{r DurationCommunity, eval = TRUE}

```

## Functional Traits

```{r DurationFunctionalGroup,  echo=FALSE}

```

## Functional Traits

```{r TimeFunctionalGroup,  echo=FALSE}

```

## Compare the treatments

```{r FirstBudSpecies, echo=FALSE}

```

## Compare the treatments

```{r TimeFsSpecies, echo=FALSE}

```

## Things to discuss

- How to define the flowering time to "early","late" stage ?
- How to define the alpine species according the elevation span?


## Next steps

- Compare microclimate (air and soil temperature and moisture) between warming treatments
- Calculate phenological "events" in degree days (days above 5C)
- Use regression to predict missing air temperature values at H site.
- Analyse phenological response in different treatments.


