---
title: "Phenology data 2016"
author: "Li Zhang and Aud Halbritter"
date: "1st. November 2016"
output: ioslides_presentation
---

## Questions and hypothesis

1. Does phenology in alpine grasslands respond to warming?
2. Do species with certain traits respond differently? Funcitonal Group, flowering time?
3. Do species respond differently to OTC and transplant?
4. How plastic are species in response to warming and cooling?


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE, fig.height = 5.5, fig.width = 8)
knitr::read_chunk("Important Figures.R")

```


## Community approach

```{r peakCommunity, eval = TRUE, echo=FALSE}

#PeakCommunity + theme_grey(base_size = 20) + theme(legend.title=element_blank()) + ggtitle("Peak")

```

```{r,  echo=FALSE}
# DurationCommunity + theme_grey(base_size = 20) + theme(legend.title=element_blank()) + ggtitle("Duration")
```

## Functional Traits

```{r,  echo=FALSE}
# PeakFounctionalGroup + theme_grey(base_size = 20) + theme(legend.title=element_blank()) + ggtitle("Peak time of different FunctionalGroup")
```

```{r,  echo=FALSE}
# TimeFounctionalGroup + theme_grey(base_size = 20) + theme(legend.title=element_blank()) + ggtitle("time between neighboring stages")
```

## Compare the treatments

```{r, echo=FALSE}

#firstbudSpecies + theme_grey(base_size = 5) + theme(legend.title=element_blank())# + ggtitle("First buds")

```

```{r, echo=FALSE}
#TimeFsSpecies + theme_grey(base_size = 5) + theme(legend.title=element_blank())# + ggtitle("...")
```

## Things to discuss

- How to define the flowering time to "early","late" stage ?
- How to define the alpine species according the elevation span?


## Next steps

- Calculate microclimate effects of different warming methods
- How species respond to experimental temperature?
- Gap of the H site climate data.


